---
title: "TNX and Currency(DXY)"
author: "Charlie"
date: "10/4/2021"
output: html_document
---

```{r setup, include=FALSE}
library(readr)
data_curr <- read_csv("C:/Users/okiki/Desktop/TimeSeries/bond yiels on currencies/data.csv")

```

### Overview of Data

```{r overview, echo=FALSE}
library(tidyverse)
#TNX Plot
tnx_plot<-ggplot(data_curr, aes(x=data_curr$Date, y = data_curr$TNX)) + geom_line()
tnx_plot +ggtitle("Ten Year Bond Prices") + xlab("Date") + ylab("Price") 

#DXY Plot
dxy_plot <-ggplot(data_curr, aes(x=data_curr$Date, y = data_curr$DXY)) + geom_line()  
dxy_plot+ ggtitle("Dollar Index ")+ xlab("Date") + ylab("Price")

#Scaled Plot of DXY and TNX
tnx_us_scaled <- ts(scale(data_curr$TNX))
dxy_us_scaled <- ts(scale(data_curr$DXY))

tnx_dxy_plot <- ggplot(data_curr)+geom_line(aes(x=data_curr$Date,y=tnx_us_scaled),colour = "red")+geom_line(aes(x=data_curr$Date, y=dxy_us_scaled), colour = "blue")
tnx_dxy_plot+ xlab("Date") + ylab("Price")

#Scatter Plot to show linear Relationship
p <- ggplot(data_curr,aes(x=TNX, y = DXY))+ geom_point() +geom_smooth(method = lm )+ scale_x_log10() + scale_y_log10()
p + ggtitle("Scatter Plot of Dollar Index and Ten Year Bond Prices") + xlab("Ten Year Bond Prices") + ylab("Dollar Index") 

```
### Stationarity

Here we check and modify the data to test for stationarity, for the purpose of generating and test univaritae models, that require stationary data. It is only the first step in identifying a model that could be used as well as how each variable affects itself given we are dealing with time series data

```{r stationarity, echo=FALSE}
library(tseries)
## test for stationarity
adf.test(data_curr$TNX)
adf.test(data_curr$DXY)
```
The results of the above test indicate the data is non-stationary as the p-value is is greaterthat a significance level of 5%(0.05) 

We therefoe followup by differencing the time series data in the next markdown, followed by another test of stationarity. This step will continue d times until the timeseries data is stationary indacated by the p-value being < (less than) 0.05.

At that point we will denote the timeseries as I(d) where d is the order of differencing

```{r stationarity2, echo=FALSE}
##Detrending non-stationary data
tnx_diff <- diff(data_curr$TNX, differences = 1)
dxy_diff <- diff(data_curr$DXY, differences = 1)

## test for stationarity
adf.test(tnx_diff)
adf.test(dxy_diff)

```
Since the test has yielded p-values < 0.05 for both variables, we can say they are stationary of order 1 denoted by I(1)


### ACF and PACF

The purpose of this two plot is to graphically represent the Autocorrelation of each wariable with k number of lags
The ACF is vey direct i its approach however the PACF removes any inderect relationships of the one lag to others in the system
```{r}

##ACF TNX
acf(data_curr$TNX, main = "Correlogram of TNX ", lag.max = 30)
pacf(data_curr$TNX, main = "Partial Correlogram of Ten Year Bond Yields", lag.max = 30)


##ACF DXY
acf(data_curr$DXY, main = "Correlogram of DXY", lag.max = 30)
pacf(data_curr$DXY, main = "Partial Correlogram of % Change in Dolla Index", lag.max = 30)

#acf(data_curr$TNX, main = "Correlogram of TNX", lag.max = 30)
#acf(data_curr$DXY, main = "Correlogram of DXY", lag.max = 30)

```
the results of the PACF indicate that there is no real relation ship between the lags, a possible indicator of the induvidual process being a martingale in nature, in that there is no information on the future

### Autocorrelation and Serial Correlation

we can Attach a value to test for correlation using both Autocorrelation and Serialcorrelation

#### Autocorrelation
Autocorrelation is the correlation between a variable and its lags 

```{r autocorrelation , echo=FALSE}
#correlation of lags 
Box.test(us_tnx, lag = 20, type = c("Ljung-Box"))
Box.test(us_dxy, lag = 20, type = c("Ljung-Box"))

```

#### Serial Correlation

Serial Correlation is the correlation between a variable's error terms and the error terms of its lags 
```{r serial correlation , echo=FALSE}

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
